---
title: "CBE-LSE Bibliometric Analysis"
author: "Caleb Trujillo, Darcie Nelson, Rachel Kudlacz, Germaine Ng"
date: "`r Sys.Date()`"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require("devtools")

devtools::install_github("massimoaria/bibliometrix")
devtools::install_github("wmurphyrd/fiftystater")
devtools::install_github("UrbanInstitute/urbnmapr")

library(urbnmapr)
library(bibliometrix)
library("fiftystater")

pacman::p_load(tidyverse,
readxl,
networkD3,
rcartocolor,
rgexf,
igraph,
xtable,
scales,
ggplot2,
sf,
ggthemes,
ggpubr,
ggrepel,
RColorBrewer)

source('functions.r')
```

## Introduction

There has been tremendous growth in the area of undergraduate biology research over the last fifteen years. This study attempts to summarize and analyze the progress of this growth for the journal of *CBE-LSE*. 

### Summary of initial data set

```{r dataset, skip = TRUE}
txt <- c("rawdata/CBE-LSE-2008-June2022/CBE-LSE-2008-June2022.txt")
data <- convert2df(file = txt, dbsource = 'wos', format = "plaintext") 

results <- biblioAnalysis(data, sep = ";")

theme_default <- theme(
    plot.caption = element_text(hjust = 0, face= "italic"),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    panel.background = element_rect(fill = "white"),
    panel.grid = element_line(size = .25, color = "grey60"),
    axis.ticks = element_blank(),
    legend.key = element_rect(color = "#F2F2F2"),
    legend.background = element_rect(fill = "white"),
    legend.position = "top",
    plot.background = element_rect(fill = "white")
    )
```

After the results are processed, they are stored as data tables for information reporting. 

```{r biblio, skip = TRUE}
options(width=100)

S <- summary(object = results, pause = FALSE)
xtable(S$MainInformationDF)

dir.create("tables")
write.csv(file = "tables/keywords.csv",as.data.frame(results$ID[1:20]))

write.csv(file = "tables/Maininformation.csv",S$MainInformationDF)

write.csv(file = "tables/ArticlesYears.csv",S$AnnualProduction)

write.csv(file = "tables/MostCitedPapers.csv",S$MostCitedPapers)

write.csv(file = "tables/MostProdAuthors.csv", S$MostProdAuthors)

write.csv(file = "tables/Universities.csv", results$Affiliations)

write.csv(file = "tables/Data.csv", data)
```

# Research Questions

### Basic overview of the field

```{r overview, skip = TRUE}
colnames(S$AnnualProduction) <- c("Year","Articles")

AnnualProduction <- S$AnnualProduction %>%
  mutate(Indexed = "Indexed") %>%
  filter(Year != 2022) %>%
  rbind( data.frame(Year = c(2021,2022), 
                    Indexed = "Projected", 
                    Articles = c(74,40 + 25 + 20))
         ) %>%
  mutate(col = case_when(Indexed == "Indexed" ~ "#266b6e",
                         Indexed == "Projected" ~ "#1d4f60",))

prodplot <- ggplot(data = AnnualProduction, 
                 mapping = aes(x = Year, 
                               y = Articles, 
                               group = Indexed, 
                               color = Indexed, linetype = Indexed)) +
  geom_line(stat = "identity", 
            size = 1.5) +
  geom_text(data = AnnualProduction %>% filter(Year %in% c(2010)), 
            aes(x = Year, y= 115, label = "Wood "), 
            color = "Black", 
            hjust = 1, 
            vjust = 1) +
  geom_line(data = AnnualProduction %>% filter(Year %in% c(2010:2020)), 
            aes(x = Year, y= 113),
            color = "Black") +
  geom_point(data = AnnualProduction %>% filter(Year %in% c(2010,2020)), 
             aes(x = Year, y= 113),
             color = "Black") +
  geom_text(data = AnnualProduction %>% filter(Year %in% c(2015)), 
            aes(x = Year, y= 114, label = "Dolan"), 
            color = "Black", 
            hjust = 0, vjust = 0) +
  geom_text(data = AnnualProduction %>% filter(Year %in% c(2020)), 
            aes(x = Year, y= 113, label = " Schinske &\n Tanner"), 
            color = "Black", hjust = 0, 
            vjust = 1, nudge_y = 0) +
  geom_text_repel(data = AnnualProduction %>% filter(Year %in% c(2010, 2016)), 
                  aes(x = Year, y= Articles, label = c(Articles)), 
                  min.segment.length = 1, vjust = "middle", 
                  hjust =1, box.padding = 0.1) +
  geom_text_repel(data = AnnualProduction %>% filter(Year %in% c(2011, 2015)), 
                  aes(x = Year, y= Articles, label = c(Articles)), 
                  min.segment.length = 1, vjust = "top", 
                  hjust = "right", box.padding = 0, 
                  nudge_x = 0, nudge_y = 0) +
    geom_text_repel(data = AnnualProduction %>% filter(Year %in% c(2013)), 
                  aes(x = Year, y= Articles, label = c(Articles)), 
                  min.segment.length = 1, vjust = "top", 
                  hjust = "right", box.padding = 0.4, 
                  #nudge_x = 0, 
                  nudge_y = 4
                  #vjust = "middle", 
                  #hjust =1
                  ) +
  geom_text(data = AnnualProduction %>% filter(Year %in% c(2022), 
                                               Indexed == "Projected"), 
            aes(x = Year, y= Articles, 
                label = "Projected\n 85"), 
            vjust = 0, hjust = 1, nudge_y = 2) +
  #geom_line(data = data.frame(x = as.factor(c(2021,2022)), y = c(74,40 + 25 + 20)), aes(x,y), linetype = 6, stat = "identity", color = "266b6e", # "#1d4f60", size = 1, alpha = 0.8) + # added projected articles.
  scale_x_discrete(breaks = function(x){x[if_else(x == 2010 | x == 2020, TRUE,FALSE,)]})+
  theme_default +
  scale_color_manual(values= c("#5881b7","#29456B")) +
   guides(Indexed = guide_legend("Published articles"))+
  theme(#panel.grid.major.x = element_blank(),
        panel.grid.minor.y =  element_blank(),
        panel.grid.major.y = element_line(size = 0.2),
        axis.text.x = element_text(hjust = 0),
         legend.position = "none")+
  labs(
    title = "Articles published per year",
    x = NULL,
    y = NULL,
  )

prodplot
ggsave("figures/AnnualProductivity.jpg", 
       device = "jpeg", dpi = 400, bg = "white",
       width = 7, height = 4, units = "in", limitsize = FALSE)


```


## Authoring

```{r author productivity}
S$MostProdAuthors 

authors=gsub(","," ",names(results$Authors))
indices <- Hindex(data, field = "author", elements = authors, sep = ";", years = Inf)

authortopH<- indices$H %>%
  dplyr::arrange(desc(h_index)) %>%
  select(Element,h_index) %>%
  top_n(10)

as_tibble(results$Authors)

authordata <- dplyr::inner_join(tibble::as_tibble(results$Authors),indices$H, by = c("AU" = "Element")) %>%
  filter("n" > 5)# %>%
  #only showing authors with at least 5 publications.

M <- data
M$TC <- as.numeric(M$TC)
M$PY <- as.numeric(M$PY)
M <- M[!is.na(M$PY), ]
Y <- as.numeric(substr(Sys.time(), 1, 4))
listAU <- (strsplit(M$AU, ";"))
nAU <- lengths(listAU)

df <- data.frame(AU = trimws(unlist(listAU)), SR = rep(M$SR,nAU))
AU <- df %>% group_by(.data$AU) %>% 
  count() %>% 
  full_join(authortopH, by = c("AU" = "Element")) %>%
  arrange(desc(.data$h_index)) %>% 
  ungroup()
k <- min(10, nrow(AU))
AU <- AU %>% slice_head(n = k)
AU$case <- str_replace(
  str_to_title(AU$AU),
  "[a-zA-Z]+$",
  str_to_upper(
    str_extract(
      AU$AU,"[a-zA-Z]+$")
    ))
  
df <- df %>% right_join(AU, by = "AU") %>% left_join(M, by = "SR") %>% 
    select(.data$AU.x, .data$PY, .data$TI, .data$SO, .data$DI, .data$TC) %>% 
    mutate(TCpY = .data$TC/(Y - .data$PY + 1)) %>% 
    group_by(.data$AU.x) %>% 
    mutate(n = length(.data$AU.x)) %>% 
    ungroup() %>% 
    rename(Author = .data$AU.x, year = .data$PY, DOI = .data$DI) %>% 
    arrange(desc(.data$n), desc(.data$year)) %>% 
    select(-.data$n)

df2 <- dplyr::group_by(df, .data$Author, .data$year) %>% 
    dplyr::summarise(freq = length(.data$year), TC = sum(.data$TC), TCpY = sum(.data$TCpY)) %>% 
    as.data.frame()

AU2 <- df2 %>% group_by(Author) %>% summarise(medianY = median(year)) %>% full_join(AU, by = c("Author" = "AU"))
AU2$case<-fct_reorder(AU2$case,
                        AU2$medianY,
                        #AU2$h_index,
                        .desc = FALSE)
  
levels(df2$Author) <- levels(AU2$case)
x <- c(0.5, 1.5 * k/10)
y <- c(min(df$year), min(df$year) + diff(range(df2$year)) * 0.125)
data("logo", envir = environment())
logo <- grid::rasterGrob(logo, interpolate = TRUE)


authorprod <- ggplot(df2, aes(x = .data$Author, y = .data$year,
                              text = paste("Author: ", .data$Author,
                                    "\nYear: ", .data$year,
                                    "\nN. of Articles: ", .data$freq, 
                                    "\nTotal Citations per Year: ", round(.data$TCpY, 2)))) + 
    geom_line(data = df2, aes(x = .data$Author, y = .data$year, group = .data$Author), 
              size = 0.7, color =  "#994E95", alpha = 0.9) + 
  geom_point(aes(size = .data$freq), color = "#FFFFFF") +
  geom_point(aes(alpha = .data$TCpY, size = .data$freq), color = "#994E95") +
    scale_size(range = c(2, 6), 
               breaks = c(1,3,5,7)) + 
    scale_alpha(range = c(0.3, 1), 
                breaks =  c(0,20,40,60)) + 
    scale_y_continuous(breaks = c(2010,2020)) +
    guides(size = guide_legend(order = 1, "Number of\n Articles"), 
           alpha = guide_legend(order = 2, "Times Cited\n per Year")) + 
  theme_default+
    theme(legend.position = "bottom",
        legend.title = element_text(),
        legend.box="vertical",
          text = element_text(color = "#444444"), 
          panel.background = element_rect(fill = "#FFFFFF"),
          axis.title = element_text(size = 14, color = "#555555"), 
          axis.title.y = element_text(vjust = 1, angle = 0, hjust = 0), 
          axis.text.x = element_text(
                                     hjust = 0
                                     ),
          axis.text.y = element_text(
                                   margin = margin(r = -0.05, l = 0.3, unit = "in"),
                                   hjust = 1),
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          panel.grid.major.y = element_line(size = 0.2),
        panel.grid.major.x = element_line(size = 0.2),
        plot.title.position = "plot", legend.margin=margin())+
            guides(fill=guide_legend(ncol = 1 ,bycol = TRUE)) + 
    labs(title = "Author productivity from 2008 - 2022", x = NULL, y = NULL) +
    scale_x_discrete(labels = rev(levels(df2$Author))) + 
  #theme_minimal() +
  #scale_x_discrete(labels = AU$case)+
  coord_flip() 

authorprod

ggsave("figures/AuthorProd.jpg", 
       device = "jpeg", dpi = 400, bg = "white",
       width = 7, height = 4.5, units = "in", limitsize = FALSE)
```




```{r combing journal and author figure}
ggarrange(prodplot + 
            ggtitle("A. Journal Productivity")#+ 
            #theme(plot.margin = margin(0.1,0.1,2,0.1, "cm")) 
            ,
                  authorprod +
                    ggtitle("B. Top-Author Productivity") #+
                    #theme(plot.margin = margin(0.1,0.1,2,0.1, "cm")) 
            , ncol	=1, align = "hv", common.legend = TRUE, legend = "right") +
            #guides(fill=guide_legend(nrow = 1,byrow = TRUE)) +
            guides(fill=guide_legend(ncol = 1,bycol = TRUE)) #+ theme(legend = element_rect(hjust = 0))

ggsave("figures/Prodcommon.jpg", 
       device = "jpeg", dpi = 400, bg = "white",
       #width = 4, height = 6, units = "in", 
       limitsize = FALSE)
```


```{r author other, eval=FALSE}
authordata %>%
  filter(n > 8) %>%
ggplot(aes( x = NP, y = h_index)) + 
  geom_point(alpha = 0.6) +
  geom_label_repel(aes(label = AU), size = 2,  box.padding = 0.001, min.segment.length = 0.01) +
  #theme_dark() +
  theme_default +
  labs(y = "h—index",
       x = "Publications",
       caption = "CBE — Life Science Education") +
  coord_flip() +
  ggtitle("Author productivity", subtitle = "Number of publications and h-index for LSE authors between 2010 and 2021")

authordata %>%
  filter(n > 8) %>%
ggplot(aes(x = reorder(AU, (NP)), y = NP)) + 
  geom_col(alpha = 1) +
  #geom_label_repel(aes(label = AU), size = 2, box.padding = 0.001, min.segment.length = 0.01)  +
  #theme_minimal()+
  theme_default +
  labs(y = NULL,
       x = NULL,
       caption = "CBE — Life Science Education between 2010 and 2021") +
  coord_flip() +
  theme(axis.text.y = element_text(size = 8),
        panel.grid.major.y = element_blank(),
        #panel.grid.major.x = element_blank(),
        #panel.grid.minor.x = element_blank(),
        legend.position = 'none') +
  ggtitle("Author productivity", subtitle = "Number of publications by LSE authors")

# Add color for school type using the other graph to depict these. 
# Going to use full join between data on author productivity and their affiliation (university or institution). 
```


## Institutions
### Affiliations around the world

```{r world affiliations, echo=FALSE}

world_map = map_data("world") %>% 
  filter(! long > 180)

countries <- world_map %>% 
  distinct(region) %>% 
  rowid_to_column()

countryfreq <- results$Countries %>%
  as.data.frame() %>%
  mutate(Tab = str_to_title(Tab)) %>% 
  mutate(Tab = case_when(
    Tab == "Usa" ~ "USA",
    Tab == "United Kingdom" ~"UK",
    TRUE ~ Tab
  )) 

AffiliationWorldMap <- countries %>%
  full_join(countryfreq, by = c("region" = "Tab")) %>% 
  ggplot(aes(fill = Freq, map_id = region), color = 1) +
  #geom_hline(yintercept=0, color = "light grey") +
  geom_map(map = world_map, colour = "white", lwd = 0.2) +
  expand_limits(x = world_map$long, y = world_map$lat) +
  coord_map("moll") +
  #coord_quickmap()+
  theme_map()+
  #theme_default +
  #labs(caption = "") +
  theme(#plot.margin= unit(c(0.5, 0.5, 0.5, 0.5), "cm"),
        # plot.caption = element_text(hjust = 0, face= "italic"),
        # plot.title.position = "plot",
        # plot.caption.position =  "plot",
        legend.title = element_blank(),
        panel.background = element_rect(fill = "aliceblue", color = "aliceblue"),
        legend.position = c(0.03, 0.06),
        legend.background = element_rect(fill = NA),
        legend.direction = "vertical",
        #legend.key.size = unit(0.4, "cm"),
        legend.key.height= unit(.5, 'cm'),
        legend.key.width= unit(.5, 'cm'),
        #plot.caption.position = "plot",
        #plot.caption = element_text(hjust = 0)
        #legend.margin = margin(6, 12, 4, 1)
        #legend.position = "left"
        ) +
  scale_fill_carto_c(palette = "BluGrn", direction = 1,
                       trans = scales::pseudo_log_trans(sigma = 0.01),
                       breaks = c(1,10, 100, 1000),
                       labels = c(1,10, 100, 1000),
                       limits = c(1,1000)
  ) +
  labs(fill = "Count of article",
       title = "Articles by author's country affiliation",
    x = NULL,
    y = NULL
    ) 

AffiliationWorldMap
ggsave("figures/AffiliationWorldMap.jpg", device = "jpeg", dpi = 400,  width = 7,
  height = 3,
  units = "in", limitsize = FALSE)
```

### Affiliations in the US

```{r US affiliations}
#Affiliation Map - US
#Joining files
msidata <- read_excel("rawdata/2020eligibilitymatrix.xlsx", 
    skip = 10)

affiliations <- read_excel("tables/UnivIndex.xlsx")

msiuniv <- left_join(affiliations, msidata) %>%
  filter(OPEID != "NA")

#Tables
msistates <- msiuniv %>%
  group_by(St) %>%
  summarize(n = n(), articles = sum(Freq) ) %>%
  #filter(!(St %in% c("MH", "PR", "VI", "GU"))) %>% 
  rename(states = St, affiliations = n) %>%
  group_by(affiliations, articles)
view(msistates)

msistates$state_name <- state.name[match(msistates$states,state.abb)]

us <- fortify(map_data("state"), region = "region") %>%
  mutate(region = str_to_title(region))
spatial_data <- right_join(msistates,
                          us,
                          by = c("state_name" ="region"))

affiliationMap <- ggplot() +
  geom_map(data  =  spatial_data, map = us,
             aes(x = long, y = lat, map_id = state_name, group = group, fill = affiliations, label = states),
             color = "black", size = 0.25) +
  coord_map("albers", lat0 = 39, lat1 = 45) +
  theme_map() +
  theme_default +
  scale_fill_viridis_c(option = "E", 
                       direction = -1)+
  labs(fill = "Author affiliations",
       title = "Number of author affilitations by state",
       x = NULL,
       y = NULL) +
  theme(plot.margin = unit(c(1,1,1,1), "cm"),
        panel.background = element_blank())

ggsave("figures/AffiliationUSMap.jpg", device = "jpeg", dpi = 400,  width = 7,
  height = 5,
  units = "in", limitsize = FALSE)


centroids <- spatial_data %>%
  group_by(state_name, articles) %>%
  summarise(latitude = exp(mean(log(lat))), longitude = exp(mean(log(long))))

#Article Map 
ArticlesUSMap <- ggplot() +
  geom_map(data  =  spatial_data, map = us,
           aes(x = long, y = lat, map_id = state_name, group = group, fill = articles, label = states),
             color = "white", size = 0.25) +
  coord_map("moll") +
  theme_map() +
  labs(fill = "Publications",
       title = "Articles by author's state affiliation",
       caption = "DC: 23, PR: 11, HI: 6, AK: 3, VI: 2, GU: 1, MH: 1.\nCounts are summarized by state/territory of each article by each author's affiliation.",
    x = NULL,
    y = NULL
    ) +
  scale_fill_carto_c(palette = "BluGrn", direction = 1) +
  theme(#plot.margin = unit(c(-2,0,0,0), "cm"),
        panel.background = element_blank(),
        legend.background = element_blank(),
        legend.direction = "vertical",
        legend.title=element_blank(),
        legend.key.height= unit(.5, 'cm'),
        legend.key.width= unit(.5, 'cm'),
        plot.caption.position = "plot",
        plot.caption = element_text(hjust = 0)
        #legend.position = "top"
        )

ArticlesUSMap
ggsave("figures/ArticlesUSMap.jpg",
       device = "jpeg", dpi = 400,
       width = 7, height = 4,
       units = "in", limitsize = FALSE)
```

```{r combining maps}
ggarrange(AffiliationWorldMap, ArticlesUSMap, legend = "right", ncol = 1, nrow = 2, align = c("hv"))
ggsave("figures/WorldUSMap.jpg",
       device = "jpeg", dpi = 400,
       width = 7, height = 8,
       units = "in", bg = "white", limitsize = FALSE)

```

```{r MSI, echo=FALSE}
msiuniv$`Eligible/ Current Grant` <- as.factor(msiuniv$`Eligible/ Current Grant`)

msieligible <- msiuniv %>%
  group_by(`Eligible/ Current Grant`) %>%
  summarize(n = n())

msiuniv$`Type & Control` <- as.factor(msiuniv$`Type & Control`)

msitype <- msiuniv %>%
  group_by(`Type & Control`) %>%
  summarize(n = n()) %>%
  mutate(percent = (n/sum(n)))

msitypeall <- msidata %>%
  group_by(`Type & Control`) %>%
  summarize(n = n()) %>%
  mutate(percent = (n/sum(n)))

types <- left_join(msitypeall,msitype, by = "Type & Control")
colnames(types)<- c("SchoolType", "Number of Insitutions in US", "US", "Number of Institutes in LSE", "LSE")

types$SchoolType <- recode(types$SchoolType, "Pri 2yr" = "Private 2-year", "Pri 4yr" = "Private 4-year","Pub 2yr" = "Public 2-year", "Pub 4yr" = "Public 4-year") 

view(types)

#We try to compare the percentage breakdown of institutions in the US according to the MSI eligibility matrix to amount in the LSE affiliations list.

#Public

types %>%
  pivot_longer(!SchoolType) %>%
  filter(name == "US" | name == "LSE") %>%
  filter(SchoolType != FALSE) %>%
  mutate(colorlevel = case_when(
      name == "US" ~ 0.9,
      name == "LSE" ~ 0.7)) %>%
  ggplot(aes(x = (name),value)) +
#  geom_col(aes(fill = SchoolType, 
#               color = scale_fill_manual(values = c("LSE" = "darkblue", "US" = "red")))) +
    geom_col(aes(fill = SchoolType, color = as.numeric(colorlevel)), 
           size = 4) +
  geom_text(aes(label = paste0(round(value*100, 0),"%")),
            vjust = 0.5, nudge_y = -.04,
            size = 3, fontface = "bold") +
  theme_default +
  theme(legend.position="none", 
        strip.background = element_rect(fill = "#F2F2F2"),
        #panel.grid.major.x = element_blank(),
        axis.text = element_text(size = 10)
        ) +
  scale_color_identity(guide = "none") +
  scale_y_continuous(minor_breaks = NULL,
                     labels = scales::percent) +
  labs(x = NULL, y = NULL,
       title = "What types of institutions are represented in LSE?"
       ) +
  facet_wrap(~SchoolType, nrow = 2) +
  theme(panel.spacing.y = unit(1, "lines"),
        axis.text.y = element_text(margin = margin(l = 0.2, unit = "in")),
        strip.text.x = element_text(size = 11),
        strip.background = element_rect(fill = "white"),
        plot.margin = margin(t = .25, r = .25, b = .25, l = .1, unit = "in"))


ggsave("figures/SchoolTypes.jpg", device = "jpeg", dpi = 400,  width = 7,
  height = 5,
  units = "in", limitsize = FALSE)


#SECOND ATTEMPT AT COLOR SCHEME

types %>%
  pivot_longer(!SchoolType) %>%
  filter(name == "US" | name == "LSE") %>%
  filter(SchoolType != FALSE) %>%
  ggplot(aes(x = (name),value)) +
    geom_col(aes(fill = value))+
    #geom_col(aes(fill = c("red",carto_pal(n = 7, "BluGrn")),
                  # c("red","#c4e6c3", "#96d2a4", "#6dbc90", "#4da284", "#36877a", "#266b6e", "#1d4f60")), 
    #       size = 4)) +
  geom_text(aes(label = paste0(round(value*100, 0),"%")),
            vjust = 0.5, nudge_y = -.04,
            size = 3, fontface = "bold") +
  theme_default +
  theme(legend.position="none", 
        strip.background = element_rect(fill = "#F2F2F2"),
        #panel.grid.major.x = element_blank(),
        axis.text = element_text(size = 10)
        ) +
  #scale_color_identity(guide = "none") +
  scale_fill_carto_c(type = "quatitative", palette = "BluGrn")+
  scale_y_continuous(minor_breaks = NULL,
                     labels = scales::percent) +
  labs(x = NULL, y = NULL,
       title = "What types of institutions are represented in LSE?"
       ) +
  facet_wrap(~SchoolType, nrow = 2) +
  theme(panel.spacing.y = unit(1, "lines"),
        axis.text.y = element_text(margin = margin(l = 0.2, unit = "in")),
        strip.text.x = element_text(size = 11),
        strip.background = element_rect(fill = "white"),
        plot.margin = margin(t = .25, r = .25, b = .25, l = .1, unit = "in"))

```


```{r MSI cont}
temp <- msiuniv %>%
  mutate_if(is.numeric,as.factor)%>%
  mutate_if(is.character,as.factor)%>%
  select(`Institution Name`,`AANAPISI`, `AANAPISI F`,`ANNH`,`ANNH F`,`HBCU`,`HBCU Masters`, HBGI,HSI,`HSI STEM`,NASNTI, `NASNTI F` ,`PBI F`,`PBI A`,PPOHA,SIP,TCCU) %>%
  pivot_longer(cols = !`Institution Name`) %>%
  mutate(eligibility = if_else(value == 1 | value == 2| value == 3, "Ineligible", "NA")) %>%
  mutate(eligibility = if_else(value == 4 | value == '4R' |value == 5 | value == '5R', "Eligible or potentially eligible", eligibility))%>%
  mutate(eligibility = if_else(value == 6, "Current grantee", eligibility)) %>%
  mutate(eligibility = if_else(value == 0, "Undetermined", eligibility)) %>%
  group_by(name,eligibility)%>%
  summarize(n=n())%>%
  mutate(perc = round(n/sum(n),3)) %>%
  mutate(titleIII = case_when(
    name == "SIP" ~ TRUE,
    TRUE ~ FALSE))

msisummary_n <- temp%>%
  select(!perc)%>%
  pivot_wider(names_from = name, values_from = c(n))
view(msisummary_n)

msisummary_perc <- temp%>%
  select(!n)%>%
  mutate(perc = label_percent()(perc)) %>% 
  pivot_wider(names_from = name, values_from = c(perc))
view(msisummary_perc)

# temp %>%
#   filter(eligibility == "Current grantee") %>%
#   arrange(perc, "desc") %>% 
#   mutate(name = as.character(name)) %>%
#   mutate(perc = case_when(name == "SIP" ~ 100,
#                           TRUE ~ perc))%>%
#   mutate(name = reorder(as.factor(name), desc(perc)), order = (perc)) %>%
#   pull(name)-> x_levels
temp$name<- factor(temp$name, levels = c("SIP","HBCU Masters", "TCCU","AANAPISI", "PBI A", "ANNH","PBI F","PPOHA","AANAPISI F", "HBGI","HBCU" ,"HSI STEM","HSI"))

MSIAffiliationPlot <- temp %>% 
  filter(#eligibility != "Ineligible" &
    eligibility != "Undetermined", 
    #eligibility != "Ineligible", 
    !is.na(name)) %>%
  ggplot(aes(x = name, y = perc, fill = eligibility)) +
  geom_col(position = position_stack(reverse = TRUE)) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) +
  coord_flip() +
  facet_grid(rows = vars(titleIII), scales = "free", space = "free")+
  #theme_dark() +
  #scale_fill_manual(values = c("#F26E50", "#F2A679", "#F2D6B9")) +
  #scale_fill_viridis(discrete = TRUE, option = "F") +
  scale_fill_manual(values = c("#266b6e", "#4da284", "#c4e6c3"
                               )) +
 #scale_fill_carto_d(palette = "BluGrn", direction = -1) +
  
  #c4e6c3,#96d2a4,#6dbc90,#4da284,#36877a,#266b6e,#1d4f60
  
  theme_default + 
  labs(
    title = "US Author affiliations by Minority Serving Institution status",
    y = NULL, 
    x = NULL
  )  +
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(margin = margin(r = -0.5, l = 0.4, unit = "cm")),
        strip.text.y =  element_blank()
       )

MSIAffiliationPlot
ggsave("figures/MsiAffiliations.jpg",
       device = "jpeg", dpi = 400,
       width = 7, height = 4,
       units = "in", limitsize = FALSE)

#mutate(status = if_else(value == TRUE, "Eligible or current grantee",  NA, status ==                     if_else(value == FALSE,"Not eligible or potentially eligible", NA)))

msiuniv %>%
  mutate_if(is.numeric,as.factor)%>%
  mutate_if(is.character,as.factor)%>%
  select(`Institution Name`,`AANAPISI`, `AANAPISI F`,`ANNH`,`ANNH F`,`HBCU`,`HBCU Masters`, HBGI,HSI,`HSI STEM`,NASNTI, `NASNTI F` ,`PBI F`,`PBI A`,PPOHA,SIP,TCCU) %>%
  pivot_longer(cols = !`Institution Name`) %>%
  mutate(eligibility = if_else(value == 1 | value == 2| value == 3, "Ineligible", "NA")) %>%
  mutate(eligibility = if_else(value == 4 | value == '4R' |value == 5 | value == '5R', "Eligible or potentially eligible", eligibility))%>%
  mutate(eligibility = if_else(value == 6, "Current grantee", eligibility)) %>%
  mutate(eligibility = if_else(value == 0, "Undetermined", eligibility)) %>%
  group_by(eligibility, `Institution Name`) %>%
  #summarise(n = n(),sum = sum(n))%>%
  unique()
    #summarise(total = sum(sum))

msiuniv%>% unique()
```

### What are the collaborative connections between institutions?

```{r top 10 affiliations}
Affiliation <- results$Affiliations[1:10]
Affiliation <- as.data.frame(Affiliation) %>%
  mutate(
    color = case_when(
      row_number() == 1 ~ "#CFB87C",
      row_number() == 2 ~ "#18453B",
      row_number() == 3 ~ "#C5050C",
      row_number() == 4 ~ "#BA0C2F",
      row_number() == 5 ~ "#4b2e83",
      row_number() == 6 ~ "#8C1D40",
      row_number() == 7 ~ "#231161",
      row_number() == 8 ~ "#2774AE",
      row_number() == 9 ~ "#7a0019",
      row_number() == 10 ~ "#a51417",
      ## all others should be gray
      TRUE ~ "#6dbc90"
    ))

#Author affiliations
ggplot(Affiliation,aes(x = reorder(str_to_title(AFF), Freq), y = Freq)) +
  geom_col(aes(fill = color)) +
  geom_col(aes(fill = "white"), alpha = 0.7) +
  geom_col(aes(y =5, fill = color)) +
  geom_text(
    aes(label = reorder(str_to_title(AFF), Freq), y=0.13),
    hjust = 0, nudge_y = 6,
    size = 3.5, fontface = "bold",
    fill = "white", label.size = 0, color="black"
  ) +
  geom_text(
    aes(label = Freq),
    hjust = 0, nudge_y = .5,
    size = 3.5, fontface = "bold"
  ) +
  coord_flip() +
  theme_default +
  labs(
    x = NULL,
    y = NULL,
    title = "Top 10 author affiliations",
  )+
  scale_fill_identity(guide = "none") +
  scale_x_discrete(labels = NULL)+ 
  scale_y_continuous(labels = NULL)+
  theme(panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.position = 'none',
        )

ggsave("figures/AffiliationsTopAuthors.jpg",
       device = "jpeg", dpi = 400,
       width = 7, height = 4,
       units = "in", limitsize = FALSE)

```

### Most cited papers and journals
```{r citations, echo=FALSE}
CR <- citations(data, field = "article", sep = ";")
CRtable <-cbind(CR$Cited[1:20])
CRtable

write.csv(file = "Citations.csv",CRtable)

# Sources Table
sourcestable <-cbind(summary(factor(CR$Source))[1:10])
sourcestable

write.csv(file = "Sources.csv",sourcestable)
```



### Multiple Correspondence Analysis

```{r conceptual structure with keywords}
# Show how key words appear together using Multiple Correspondence Analysis
#Consider selecting only articles that have the keywords  associated 
CS30 <- bibliometrix::conceptualStructure(data, 
                          field ="ID", 
                          ngrams = 1, 
                          method = "MCA", 
                          minDegree= 30,
                          clust= "3", 
                          k.max=5, 
                          stemming= FALSE, 
                          labelsize=10, 
                          documents=10
                          )

CS19 <- bibliometrix::conceptualStructure(data, 
                          field ="ID", 
                          ngrams = 1, 
                          method = "MCA", 
                          minDegree= 19,
                          clust= "3", 
                          k.max=5, 
                          stemming= FALSE, 
                          labelsize=10, 
                          documents=10
                          )


ggsave("figures/CS30ConceptualStructure.png", plot = CS30$graph_terms, device = "png")

ggsave("figures/CS30ConceptualCluster.png", plot = CS30$graph_dendogram + coord_flip(), device = "png")

ggsave("figures/19ConceptualStructure.png", plot = CS19$graph_terms, device = "png")

ggsave("figures/19ConceptualCluster.png", plot = CS19$graph_dendogram + coord_flip(), device = "png")
```


```{r title topics}
hypened<-results$ID[results$ID>10] %>%
  row.names()%>%
  str_detect("-") 
spaced<- results$ID[results$ID>10] %>%
  row.names()%>%
  str_detect(" ")
compound<-results$ID[results$ID>10][hypened|spaced]%>%
  row.names()

compound <- compound[!compound %in% "UNDERGRADUATE RESEARCH EXPERIENCES"]
  
TitleTerms <- termExtraction(data, "TI",stemming = TRUE, keep.terms = compound) %>%
KeywordGrowth(Tag= "TI_TM", top = 1000) %>%
  pivot_longer(cols = !c('Year')) %>%
  group_by(Year) %>%
  mutate(sum = sum(value), perc = value / sum) %>%
  filter(value > 1) %>%
  filter(perc > 0.005)

SharedTerms <- TitleTerms %>%
  #select(Year,name) %>%
  group_by(name) %>%
  summarize(total = n()) %>%
  filter(total > 2)

TopTerms<- TitleTerms %>% 
  filter(name %in% SharedTerms$name) %>%
  group_by(Year) %>%
  arrange(value, .by_group = TRUE) %>%
  top_n(15)

TitleText <- TitleTerms %>%
  group_by(name) %>%
  top_n(1, Year) %>%
  filter(name %in% SharedTerms$name)

TitleTerms %>% 
  filter(name %in% TopTerms$name) %>%
  ggplot(aes(Year, perc, group = name, color=name, fill=name, label = name))+
  geom_line() + 
  geom_text_repel(aes(label = name), data = . %>% group_by(name) %>% top_n(1, Year), 
                  size = 2, 
                  color = "black",
                  arrow = arrow(length = unit(0.02, "npc")),
                  box.padding = 0.5
                  )# + 
  #scale_y_log10(labels = label_percent()) + 
  
  #theme_default +
  labs(title = "Conceptual trends based on article titles")+
  theme(legend.position="none")

ggsave("figures/TitleLineTrends.png", device = "png", dpi = 400,
       width = 7, height = 7,
       units = "in")


TitleTerms %>% 
  filter(name %in% TopTerms$name) %>%
  ggplot(aes(x=reorder(as.factor(str_to_sentence(name)),cumsum(value)),y = Year, group = name, color=name, fill=name, label = name, size = perc), alpha = 0.3)+
  #geom_violin(alpha = 0.3)+
  #geom_point() +
  #geom_line(alpha = 0.8, size = 0.5)+
  geom_violin(aes(scale = perc))+
  geom_text(aes(label = str_to_sentence(name)), data = . %>% group_by(name) %>% top_n(-1, Year), #%>% filter(Year > 2012), 
                  size = 2, 
                  color = "black",
                  #arrow = arrow(length = unit(0.02, "npc")),
                  #box.padding = 0.5
                  nudge_x = 0,hjust = -0)+
  scale_y_continuous(labels = label_date(format = "%y")) +
  scale_x_discrete()+
  coord_flip ()+
  theme_default +
  labs(title = "Conceptual trends based on article titles", y = NULL, x = NULL, )+
  theme(legend.position="none",
        axis.text.y = element_blank())

ggsave("figures/TitleTrends.png", width = 4, height = 7, device = "png")
```


```{r conceptual structure with titles, skip = TRUE, eval = FALSE, echo = FALSE}
CS2 <- termExtraction(data, "TI",stemming = FALSE, keep.terms = compound) %>%
  conceptualStructure(field ="TI_TM", 
                          ngrams = 1, 
                          method = "MCA",
                          quali.supp = NULL,
                          quanti.supp = NULL,
                          minDegree= 50,
                          clust= "auto", 
                          k.max=5, 
                          stemming= FALSE, 
                          labelsize=10, 
                          documents=2)

ggsave("figures/ConceptualStructure2.png", plot = CS2$graph_terms, device = "png")


ggsave("figures/ConceptualCluster2.png", plot = CS2$graph_dendogram + coord_flip(), device = "png")
```
